Intrusion Detection with \\ Genetic Algorithms and Fuzzy Logic

### 2013-11-07 Talk/Presentation.tex
Added more to the fuzzy logic slide.

\subsection{Fuzzy Logic}
\begin{frame}
  \frametitle{Fuzzy Logic}
  \begin{columns}
  \begin{column}{0.6\textwidth}
  \begin{itemize}
  	\item Used to detect patterns that have a behavior that is between normal and unusual.
  	\item Fuzzy logic rule: If <\emph{condition}> then <\emph{consequence}>.
  	\begin{itemize}
  		\item \emph{condition} is a fuzzy variable
  		\item \emph{consequence} is a fuzzy set
  	\end{itemize}
  \end{itemize}  
  \end{column}

  \begin{column}{0.4\textwidth}
  \includegraphics[width=0.95\textwidth]{../triangleFigure.JPG}
  \end{column}
  \end{columns}
\end{frame}

@@

  \begin{column}{0.6\textwidth}
  \begin{itemize}
  	\item Fuzzy algorithm
  \end{itemize}

>>>>

\subsection{Fuzzy Logic}
\begin{frame}
  \frametitle{Fuzzy Logic}

  \begin{itemize}
  	\item Used to detect patterns that have a behavior that is between normal and unusual.
  	\item If <\emph{condition}> then <\emph{consequence}>.
  	\begin{itemize}
  		\item \emph{condition} is a fuzzy variable and \emph{consequence} is a fuzzy set
  	\end{itemize}
  	\item If the number of packets with the same destination address is 20, and $a$=10, $b$=25, $c$=45, then the degree=.6 and the region=B so the number of packets=medium.
  \end{itemize}

  \begin{columns}
  \begin{column}{0.4\textwidth}
      \includegraphics[width=0.95\textwidth]{../triangleFigure.JPG} 
  \end{column}

  \begin{column}{0.6\textwidth}
  \begin{algorithmic}
	\IF{x is between $a$ and $b$}
		\STATE{degree = $(\textrm{x}-a)/(b-a)$}
	\ELSIF{x is between $b$ and $c$}
		\STATE{degree = $(c-\textrm{x})/(c-b)$}
	\ELSE \STATE{degree = 0.0}
	\ENDIF
  \end{algorithmic}
  \end{column}
  \end{columns}
\end{frame}

@@

  \begin{column}{0.6\textwidth}
%  \begin{itemize}
%  	\item Fuzzy algorithm
%  \end{itemize}
